---
title: "Balance Communication Project"
author: "Levi_Bagwell"
date: "April 16, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Goals: Create a code using python that will communicate with a balance, take readings at certain time intervals, and also put those readings into a .csv file.

Part 1: Levi - Establish communication with balance. 
```{r}

```
Resources Consulted: 
- Balance Communication (instructables.com)
- Software Interfaces Sartorius Balances to PC(windmill.co.uk)
- Balance Communication Software WinCT (Balances.com)
Notes: At this point in our project I am trying to do some research on how people have been able to interface with various brands of balances. This information will hopefully give me insight on what to look for and where to start when beginning the process of interfacing with the balance that we have on hand. 

Part 2: Gus - Design code to take readings at certain time intervals
#For the function i am contributing to, i am looking into possible software that will allow the scale to send the readings into a CSV file. I have been specifically looking into RsWeight programs to help with the issue. In the program, one can set many perameters and take readings at specific intervals. There is options in this program to export to an Excell file and have the data arranged respectively. Need to see what components are required for the specific program and if its a possibility.
```{r}

```
Resources Consulted:
- Software info (https://www.aandd.jp/products/software/winct.html)
Part 3: Emily - Design code to insert readings into certain parts of a .csv file.
```{r}

```
Resources Consulted:
